The Astropy Project

### 2017-10-27 main.tex
typo

The \package{astropy.nddata} supackage provides three types of functionality: an abstract interface for representing generic arbitary-dimensional datasets intended primarily for developers of other packages and concrete classes building on this interface and utilities for manipulating these kind of datasets.

>>>>

The \package{astropy.nddata} supackage provides three types of functionality:
an abstract interface for representing generic arbitrary-dimensional datasets
intended primarily for developers of other packages and concrete classes
building on this interface and utilities for manipulating these kind of
datasets.
